FTLR proof cases

### 2018-05-23 fully-abstract-comp/ftlr-proof-cases.tex
Remove some duplicate lemmas.
fixed mistake in ftlr proof (related to wrong E-rel def used)
Minor changes.

\subsection{Lemmas}
In this section, I have listed lemmas that seem to be necessary for the FTLR proof.
\begin{lemma}[non-expansiveness of relations]
  \label{lem:non-expansive}
  If $n' \leq n$, then
  \begin{itemize}
  \item If $\npair{(b,e)} \in \readCond{\lin,W}$, then $\npair[n']{(b,e)} \in \readCond{\lin,W}$.
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$, then also $\memSat[n']{(\ms_S,\stk,\ms_\stk,\ms_T)}{W}$.
  \end{itemize}
\end{lemma}

@@

\begin{lemma}[$\lrol$ closed under target language antireduction]
  For all $\Phi_S$, $\Phi_T$, $\Phi_T'$, $j$, $n$, if
\[
  \Phi_S \nstep[j]{\gc} \Phi_S' \text{ and } \npair[n-j]{(\Phi_S',\Phi_T)} \in \lrol,
\]
then
\[
  \npair{(\Phi_S,\Phi_T)} \in \lrol
\]
\end{lemma}

@@

\begin{lemma}[purePart is idempotent]
  For all $W$, $\mathit{purePart}( \purePart{W} ) = \purePart{W}$
  \label{lem:purePart-idempotent}
\end{lemma}
\begin{proof}
  Follows easily from the definition.
\end{proof}

>>>>

\subsection{Lemmas}
In this section, I have listed lemmas that seem to be necessary for the FTLR proof.
\begin{lemma}[non-expansiveness of relations]
  \label{lem:non-expansive}
  If $n' \leq n$, then
  \begin{itemize}
  \item If $\npair{A} \in \readCond{\lin,W}$, then $\npair[n']{A} \in \readCond{\lin,W}$.
  \item If $\npair{A} \in \stackReadCond{\lin,W}$, then $\npair[n']{A} \in \stackReadCond{\lin,W}$.
  \item If $\npair{A} \in \writeCond{\lin,W}$, then $\npair[n']{A} \in \writeCond{\lin,W}$.
  \item If $\npair{A} \in \stackWriteCond{\lin,W}$, then $\npair[n']{A} \in \stackWriteCond{\lin,W}$.
  \item If $\npair{A} \in \execCond{\lin,W}$, then $\npair[n']{A} \in \execCond{\lin,W}$.
  \item If $\npair{A} \in \xReadCond{\lin,W}$, then $\npair[n']{A} \in \xReadCond{\lin,W}$.
  \item If $\npair{(w,w')} \in \lrvg{\trust}{W}$, then $\npair[n']{(w,w')} \in \lrvg{\trust}{W}$.
  \item If $\npair{(w,w')} \in \lrrg{\trust}(W)$, then $\npair[n']{(w,w')} \in \lrrg{\trust}(W)$.
  \item $\memSat{(\ms_S,\stk,\ms_\stk,\ms_T)}(W)$, then also $\memSat[n']{(\ms_S,\stk,\ms_\stk,\ms_T)}(W)$.
  \end{itemize}
\end{lemma}

@@

\begin{lemma}[$\lrol$ closed under source language antireduction]
  For all $\Phi_S$, $\Phi_T$, $\Phi_T'$, $j$, $n$, if
\[
  \Phi_S \nstep[j]{\gc} \Phi_S' \text{ and } \npair[n-j]{(\Phi_S',\Phi_T)} \in \lrol,
\]
then
\[
  \npair{(\Phi_S,\Phi_T)} \in \lrol
\]
\end{lemma}

@@
